% Chapter Template

\chapter{Literature Review} % Main chapter title

\label{Chapter2} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Introduction}

In this section the previous work in the field will be explored. This will give the reader adequate understanding of where 
advances in the research area can be made.\todo{Write intro to the lit review}

\medskip
This is a list of things that need to be in a lit review:
\begin{itemize}
    \item Introduction
    \begin{itemize}
        \item Why are you writing the review, and why the topic is important
        \item the scope of the review - what aspects of the topic will be discussed
        \item the criteria used for your literature selection (types of sources used and dates etc.)
        \item the organisational structure of the review
    \end{itemize}
    \item Body Paragraphs
    \begin{itemize}
        \item historical background
        \item methodologies
        \item previous studies
        \item mainstream vs. alternative viewpoints
        \item principal questions being asked
        \item general conclusions being drawn
    \end{itemize}
    \item Conclusion 
    \begin{itemize}
        \item Main agreements and disagreements of the literature
        \item any gaps or areas of further research
        \item my overall perspective on the topic
    \end{itemize}
\end{itemize}
\medskip
Checklist for a literature review. Have I:
\begin{itemize}
    \item Outlined the purpose and scope
    \item Identified appropriate and credible (academic/scholarly) literature
    \item Recorded the bibliographical details of the sources
    \item Analysed and critiqued your readings
    \item Identified gaps in the readings
    \item explored methodologies / theories / hypotheses / models?
    \item discussed varying viewpoints
    \item written an intro, body and conclusion
\end{itemize}
\bigskip
Items that I want to cover in the Lit review
\begin{itemize}
    \item Using SDR (USRP) to receive GPS signal
    \item Using SDR to transmit GPS signal
    \item Algorithms for generating spoofed signal
    \item GPS Anti-spoofing techniques
    \item GPS spoof detection techniques
    \begin{itemize}
        \item This will be what will need to be overcome in the implementation of the spoofing transmitter.
    \end{itemize}
    \item OPTIONAL: Difference between Block II and block III satellites
\end{itemize}
\medskip
Previous research into the use of SDR (software defined radio) for GPS spoofing uses has lead to common conclusions.
That is, that the use of open sourcecannot  software to ease the development. Namely multiple previous attempts at GPS spoofing
used the GNSS-SDR program for reception and the gps-sdr-sim for transmission. Both of these are available from GitHub as free
and open source programs. The issue of GPS spoofing is not uniquly that of position. Since GNSS systems have highly accurate time keeping
facilities, in the form of atomic clocks, they are used to maintain accurate time of critical infrastructure like \todo{list things that rely on GPS timing}\\

Spoofing can be defined as an intentional interfering signal that aims to make GNSS receivers produce incorrect positoning data\cite{RN8}.
\emph{GPS Spoofing has been researched actively for over 12 years and yet there doesn't seem to be any wide spread anti-spoofing technique adoption.}\todo{remove}

\bigskip
From literature the consensus is that the same thing that has made GPS ubiquitous with navigation and 
positioning has also made it a simple target for exploitation and manipulation, that is the workings
of the infrastructure are well known and public and are transparent and predictable \cite{RN7} \cite{RN4}. This is problematic since this infrastructure
is seen as a critical service by many industries including utility management, healthcare/ emergency services and security.
Having such a system so prone to threats is not ideal. The further development of SDR platforms has driven down the cost of launching
such exploits. Devices such as the HackRF, USRP, BladeRF and others have been documented for this use \cite{RN4} \cite{RN9}.

\medskip

An issue that arises when attempting to spoof a mobile device is that these devices are also able to determine locaiton based off of
network connection. \todo{insert citation for finding location from cellular/wifi connection}
K. Zeng et al. \cite{RN9} found that when these kinds of devices registered a difference in location between network based and GPS based
that they would prioritise the GPS based location. \todo{I think this is wrong}\emph{This is less of an issue than at first glance since the prevalence of VPN (virtual private networks)
are increasing for surcumventing geolocking features. Therefore to ensure that GPS locaiton services still function when a VPN is active
the GPS position should be prioritised.} There are other methods of detecting a faulty GPS signal in software and hardware that are
more accurate and allow for more flexibility of the device usage. 

\bigskip

\citeauthor{RN12} \cite{RN12} commented on the effect of GNSS spoofing of a cooperative victim. That is when someone is willing to aid the attacker
in performing an attack. This may be implemented to circumvent position based restrictions or if being GPS tracked during certain activities.
\citeauthor{RN12} used the example of a fisherman wanting their GNSS receiver to falsely report the boad had stayed out of protected areas. 

\bigskip

%-----------------------------------
%	SECTION 2
%-----------------------------------
\section{Annotated Bibliography}
%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Spoofing Attack References}

\textbf{\emph{Hijacking Unmanned Aerial Vehicle by Exploiting civil GPS vulnerabilities Using SDR} by X. Zheng et al.}\\
As written by X. Zheng et al. \cite{RN4} there has been an exponential increase in the number of UAV vehicles being used in recent times.
This increase has been driven by the advent of aerial photography of both professionals and amateurs since the cost of entry is so low. There are
also companies looking to implement delivery services using UAV, or drone, technology.
This poses security and safety concerns with such vehicles having such a reliance on GPS for accurate positioning. Having such an open and transparent
infrastructure such as that of GPS makes the signals easy to reproduce for nefarious purposes. Adding to the concern is the increase in 
affordable and high performance SDR platforms as well as open source software packages designed to minimise complexity of performing such tasks. X.Zheng et al.
showed that performing spoofing attacks on UAV vehicles is cheap and simple to control. Zheng performed 3 different hijacking attacks on the target
UAV, namely forcing the drone to land, guiding the drone to an attacker dictated area and forcing the drone to land in an attacker dictated area.
Two of the attack methods were successful at a rate of approximately 80\% and 90\%. The unsuccessful test was attempting to force the drone to land in a specified location by exploiting the 
'go home' safety feature. This requried jamming the communicaiton channel between the controller and drone. After experimentation it was shown
that this required advanced hardware and methods to achieve. Zheng also provided some recommendations for improving the security of the GPS system of, in particular
DJI Phantom 3 drones.
Future works would improve the success rate of the attacks that were successful as well as decrease the time for a successful attack. Work could 
also be put into jamming the control channel between the controller and drone.

\medskip

\textbf{\emph{Practical GPS location spoofing attack in Road Navigation} by K. Zeng et al.} \\
K. Zeng et al. provide insight into the security concerns of leaning so heavily on the GPS system in general, and more important to this
paper is the reliance on GPS for navigation. In their paper \cite{RN9} K. Zeng et al. were able to develop a practical algorithm
implementation for road network modelling and navigation spoofing using GPS. The attack model used was a hardware based approach. 
The proposed attack strategy leveraged a lunch box sized portable spoofer with the HackRF at the heart of the device. Alot of the effort
of this paper went into the production of the dynamic modelling of road network algorithm. This was done using an XML (extensible markup language)
version of an area of streets as provided by OpenStreetMap. The documentation of this algorithm will become 
useful when moving from a static based spoof attack to a dynamic one.

\medskip

\textbf{\emph{GNSS-SDR: An Open Source tool for Researchers and Developers} by C. Fern\'andes-Prades} \\
The software has undergone continual development since this paper was written. Therefore more recent version of article should be found.
Although information may still be relevant \cite{RN16}.
In 2011 C. Fern\'andes-Prades et al. developed an open source piece of software for the development and implementation of software defined radio based
GNSS receivers. At the time there was a void of accessible software radio solutions that allowed the used to investigate how a GNSS receiver worked.
The author mentions existing commercial products, as they allow for the useage of the data that GNSS systems provide.
The paper walks through the architecture of the GNSS-SDR program.

\medskip

\textbf{\emph{GPS Vulnerability to Spoofing Threats and a Review of Antispoofing Techniques} by A. Jafarnia-Jahromi} \\
In 2012 \textcite{RN6} noted that with the dependancy that society has developed on GPS it has become a viable attack target. One type attack is
so called spoofing. Spoofing and anti spoofing algorithms and techniques have become an area of interest for researchers of late. \citeauthor{RN6}
investigated the different spoofing and antispoofing techniques avaialble. The author noted that spoofing attacks can be divided into 3 main categories:
GPS signal simulator, Receiver-Based spoofers and Sophisticated Receiver based spoofers. These attack strategies come about because of vulnerabilities in the GPS system.
These vulnerabilities can be described in teh three opoerational layers of GPS, signal processing, data bit, and position/navigation solutions.
Antispoofing can be broken down into 2 groups spoof detection and spoof mitigation, with each of these being able to be further broken into subcategories.
The effectiveness of each spoof detection technique was tabulated and compared. As was the spoof mitigation techniques. Each detection and mitigation
method was given a complexity, effectiveness and spoofing sceario generality rating with notes made about the recived capability requirements.
Testing spoofing techniques is difficult to achieve since there are regulations around the emmision of EM radioation at certain frequencies and power levels.
There were three methods used to test the spoofing/antispoofing techniques. These were Indoor retransmission, spoofing using recorded data (No RF transmission), and
using RF combiners to combine authentication and spoofed signals.
The results that were acquired showed that the commercial GPS receivers were vulnerable to a number of spoofing techniques. It was also
shown that with modest, low complexity spoof detection and mitigation strategies some of the spoof attacks were able to be overcome.

\medskip

\textbf{\emph{\citetitle{RN23}} by \citeauthor{RN23}} \\
In \citeyear{RN23} \citeauthor{RN23} \cite{RN23} showcased the development of a civilian GPS spoofing device as a means of assessing the potential spoofing 
threat at the time. The main outcome of this experiment was to see the effects and help to develop future defences against spoofing attacks. In addition to 
presenting a spoofing device analyses of the GPS spoofing threat assesment and spoofing defence technqiues was also provided. 
The design of the spoofer module, which was a software component of the receiver, was described in detail. This infomation will be of great use for understanding 
DSP and GPS spoofing although it out of the scope of this section. 
The threat assesment of GPS signal spoofing was summarised into three categories, simple, intermediate and sophisticated attacks. A simple attack is that from a
GNSS signal generator, intermediate from a softare radio and complex was in the form of coordinated attack by multiple phase locked radios. 
Spoofing defences suggested at the time of publish were as follows; Data bit latency defence and vestigial signal defence.

Sophisticated attacks were found to be effective against commerical GPS units and many anti-spoofing techniques with cryptographic methods being the most 
effective way of circumventing the attacks.

This spoofing device was developed on a DSP platform, which at the time was an appropriate choice. Given the leap forward in power and flexibility
of SDR platforms since this paper was published it should be noted that the use of an SDR for this purpose would be recommneded. At the time of publish
it was noted that the cost of including multi band spoofing capabilities to a spoofing device would be prohibitvely expensive. This again has been made accessible
by SDR platforms. 

\medskip

\textbf{\emph{\citetitle{RN21}} by \citeauthor{RN21}} \\
In \citeyear{RN21} \citeauthor{RN21} \cite{RN21} developed a system to perform a series of spoof attacks on UAV's based on an SDR \cite{RN23}. The goal of this was to be able to 
control the flight path of the UAV without raising any alarm's from the victim. This paper establishes the required conditions in which a UAV will
be succeptible to being captured from a spoofing attack, as well as the range of post capture control that the spoofer will have over the victim.
From testing it was found that spoof attacks were successful from up to 50m and upto a velocity of 10m/s.
Simulations were produced for analysis of post capture control of the UAV. 
When testing, both covert and overt spoofing methods were used, distuinguished by whether or not the spoofer made an attempt to avoid detection. 
For the most part there was no practical difference between covert and overt methods since the commercial GPS units did not trigger any anti spoof mechanism when being subjected to an overt attack.
Field testing showed that the spoof attempt caused unrecoverable navigation errors which resulted in the UAV crashing. 

\medskip
%-----------------------------------
%	SUBSECTION 2
%-----------------------------------
\subsection{Anti-Spoofing References}
%-----------------------------------
%	SUBsubSECTION 1
%-----------------------------------
\subsubsection{Spoofing Detection}

\textbf{\emph{GNSS Spoofing and Detection} by M. Psiaki et al.} \\
\textbf{This is a really good reference for the state of play in the spoof attack and defence landscape. Spend time reading about the techniques and 
gain an understanding} \todo{Add comparison to \cite{RN11}}.\\
In 2016 M. Psiaki et al. \cite{RN12} reviewed the state of GNSS spoofing and spoofing defences. Since 2008 there has been an ever increasing 
interest in GNSS spoofing. A spoofer could potentially target both military and civilian infrastructure including aircraft or marine vessels which
rely on GNSS signals especially in low visibility conditions. Civilian infrastructure like cell phone towers, power grid monitoring and stock markets
use GPS signals for precise timing. This paper looks at the details of the current methods of implementing a GPS spoof attack as well as the details
of known anti spoofing techniques. Attack methods tested were self consistent spoofer, Meaconing and estimate and replay attacks, other advanced techniques.
Defence techniques can be broken down into three categories; pseudorange RAIM (receiver autonomous integrity monitoring),
looking at the difference between a true and spoofed signal, and looking for interaction between true and spoofed signals. Pseudorange RAIM is considered
too weak against modern spoofing attacks and was not considered in this publication. The specific methods of defence tested in this paper  
were advnaced signal processing techniques, encryption based, drift monitoring, signal geometry and multi pronged spoofing defence.
A \todo{include table in lit review}table was generated to visualise which defence stratagies were effective against which attack strategies. 
It was found that all attack strategies that were used in the report were effective against COTS (commercial off the shelf) GNSS receivers. The authors
recommend COTS GNSS receiver producers implement, at a minimum, a rudamentary defence strategy against spoof attacks. 

\medskip

\textbf{\emph{Spotr: GPS Spoofing detection via Device Fingerprinting} by M. Foruhandeh et al.}\\
As discussed in \cite{RN7} GPS (Global Positioning System) has become the de facto positioning infrastructure for civilian and 
military usage and while there are other satellite based positioning systems that are becoming more popular (GLONASS, Galileo, BeiDou) GPS is 
still the one that most people think of when thinking about GNSS. GPS provides this service globally and efficiently although through its ubiquity
security concerns have become apparent. Attacks have been carried out in both an academic and industry setting.
The authors believed that strengthening of the GPS framework against manipulation and exploitation must be a priority.
Proposed methods of hardening GPS have been previously proposed, however these were typically abandoned due to expense, complexity, cost or lack of robustness. 
A method of creating unique satellite "fingerprints" was developed and tested against all known spoofing attacks at time of publish.
This fingerprint algorithm was able to determine if a transmission was authentic or spoofed.
This fingerprinting algorithm implementation was found to be fast, simple, cost effective and robust when compared to previous hardening attempts. \todo{Fact check the claims of the paper} 

\medskip

\textbf{\emph{\citetitle{RN10} by \citeauthor{RN10}}} \\
In \citeyear{RN10} \citeauthor{RN10} \cite{RN10} proposed a method for detecting the presence of GPS spoofing signals through the use of two or more recievers. 
Previous literature had investigated the use of spoof detection using single receivers. These techniques were varied and ranged from simple methods like monitoring the 
power level of the received signal, to more complex like analysing the presence of vestigial peaks in the correlator output. There have also been methods proposed
that compare signals with that of non-GPS signals for example an IMU. 
The multi receiver design that \citeauthor{RN10} proposed works on the principal that the recived signal from a spoofing source will have identical characteristics (reletive time of arrival)
at each of the receivers. When there is no spoofer present there will be unique signal characterstics at each of the receivers.
The concept of detecting a spoofing event was to compare the position of each receiver against the known reletive postions. This was chosen as it will not reuqire any 
hardware modifications and the software processing can be done by an external processor, making it suitable for retrofitting to existing systems.
Four simualtions were tested from a Neyman-Pearson perspective \todo{add in a info about neyman pearson in electrical eng} (1) two receivers with known absolute locations, (2) two recievers with known separation and orientation but unknown absolute location, 
(3) two receivers with known separation and unknown orientation and absolute loaction and fianlly (4) three receiver example. The testing was performed under the assumption
that the spoofing transmitter only had one antenna.
In the first case there was approximatelty 1\% chance of a false alarm while the probability of detecction was found to be intractable.
\todo{results}

\medskip

\textbf{\emph{\citetitle{RN1}} by \citeauthor{RN1}} \\
In \citeyear{RN1} \citeauthor{RN1} \cite{RN1} proposed a method of GPS spoof detection that would allow for the localisation
of the source to be determined. Specifically this method is designed to work with vehicular GPS systems and uses existing 
V2V (vehicle to vehicle) commuiniations systems. Using a network of cooperative vehicles the spoofer could be localised by analysing the respective
Doppler shifts. After labratory testing on stationary spoofers, it was found to be effective at providing an approximate location at up to 200m away.
When the spoofer was moving, this was decreased to 50m and was movement direction agnostic. To confirm these results an experimental setup would need
to be created and experiments run. It would be expeccted that the real world results would not be as favouarble as the simulated ones, since a number of
assumptions were made that simplified the simulations. For example the spoofer was moving with a constant velocity in a perfectly straight line.

\medskip
%-----------------------------------
%	SUBsubSECTION 2
%-----------------------------------
\subsubsection{Spoofing Mitigation}

\textbf{\emph{A Low complexity GPS anti-spoofing method using multi antenna array} by S. Daneshmand et al.} \\
In 2012 S. Daneshmand et al. \cite{RN8} proposed a low computational complexity anti spoofing module for use with GPS receivers.
It was mentioned that previous anti-spoofing reasearch was done in two categories, spoofing detection and spoofing mitigation.
Most of the effort has been put into spoofing detection algorithms and less on mitigation techniques. 
Previous proposed spoofing mitigation devices used the fact that GPS spoofing devices typically transmit multiple PRN's. 
Therefore comparisons can be made between the spoofed and authentic signals. Although this is computationally complex. This proposed
device uses a multi antenna array to find the signal with most power and beam form in such a way that the antenna null is pointing in
that direction. This relies on the assumption that spoofed signals will have a measurably higher spatial energy than that of the authentic signal
as well as the authentic signal propogating from an area that is not also covered by an antenna null. Although this cannot be guarenteed.
To maximise the perfomance of the module, the authors also propose a technique to amplify the authentic signals as well as reduce the noise floor level.
S. Daneshmand mentioned that with some minor modifications the proposed module would be able to opearate with GLONASS and Galileo systems aswell. 

\medskip

\textbf{\emph{Practical Cryptographic Civil GPS signal authentication} by K. Wesson et al.} \\
K. Wesson et al. \cite{RN13} proposed a method for counteracting GPS spoofing on the popular GPS civil band. The proposed method would use cryptographic
authentication based techniques to ensure that signals were not fake and did orginate from an autorised source.\todo{write more}
\citeauthor{RN13} provided a detailed overview of the entire cryptographic authentication system.
The method employed by \citeauthor{RN13} included adding digital signatures within the GPS civil navigation message. This type of cryptographic defence
will secure the receiver against replay spoof attacks. Authentication of each civil GPS signal is performed every 5 minutes.
For the proposed authentication strategy a $P_D$ of >0.97 was achieved over the range of $37$-$51 dB-Hz$.
The implementation of such a system would require modifications to the GPS satellite system themselves, as well as a redesign of GPS receivers.
The modifications required for the GPS recievers were documented in detail in \cite{RN13}. For systems that can not easily or readily upgraded to
take advantage of these improvements an external device called "The GPS Assimilator", as proposed in \cite{RN19}, could be used to clean the incomming
signals.
Although it was noted that receivers based on SDR platforms would be able to implement the authentication algorithm easily.

\medskip

\textbf{\emph{\citetitle{RN17}} by \citeauthor{RN17}} \\
In \citeyear{RN17} \citeauthor{RN17} \cite{RN17} noted that the GPS navigation system is susceptible to electro magnetic interference. Sources of interference 
can either be natural or artifical including malicious sources (spoofing). This has the potential to threaten the reliabilty of the system which has become 
vital in accurate position and timekeeping purposes. One such use is within modern vehicles for positioning, navigation and automation. 
CACC (Cooperative Adaptive Cruise Control) systems are an evolution of ACC (Active cruise control) and include a communication stack for V2V (vehicle to vehicle) communicaiton. 
Vehicles that have a CACC system thus have a number of other sensors which are able to provice situational awareness. These include the formentioned radio
communications equipment as well as Lidar, radar, camera  IMU's (inertial measurement unit) and access to CAN data from the vehicle systems.
\citeauthor{RN17} devised a method of maintaining awareness of position from a combination of GPS signal as well as the other sensors as part of
the various other systems integrated into the vehicle and from other vechiles. It was shown experimentally that the COTS receivers were susceptible to
to spoofing attacks. It was also shown that the proposed method of spoof detection and removal was effective. Furhter work will need to be done
to test the defence method on more spoof attack methods. To ensure that this design becomes viable for the commercial world it must also work in real time.

\medskip

\textbf{\emph{\citetitle{RN18}} by \citeauthor{RN18}} \\
In \citetitle{RN18} \citeauthor{RN18} \cite{RN18} pointed out that there is a cycle of new spoofing attack strategies and then counter-measures
against them. A sudden outage to GNSS systems would have a large impact on society. \citeauthor{RN18} provided a list of GNSS-reliant ecosystems including
autonomous transportation, cellular networks and power systems. Disruptions to especically the later two would have a measureble impact. Therefore, it is
important to ensure that receviers of GNSS signals are resilient to intentional and unintentional interference.
Typical COTS GNSS receviers do not have a way of being upgraded since their hardware is set and not able to change. Having a receiver
with upgradable hardware, such as that found in SDR platforms, would make for an ideal GPS reciever. As such SDR's are well suited as GNSS receivers,
however, they are challenged by processing the GNSS data and anti spoofing method. \citeauthor{RN18} performed experiments to see how effective SDR 
platforms were at implementing a mitigation strategy in real time. A reduced complexity MMSE (minimum mean squared error) algorithm was developed for
use on the in house developed SDR platform. This algorthim was compared against MF (matched filter) techniques. It was found that at an ISR (interference to signal ratio)
of 30dB that MF correlators were unable to recive any useable signal, with BER (bit error rate) of approximatelty 50\%. Using the proposed maximise
correlator, at a 30dB ISR, showed a BER gain of approximately $10^5$. 
However, in testing it was found that most COTS receivers were not able to perform these duties in real time due to the increase in complexity of the antispoofing algorithms.

\medskip

\textbf{\emph{\citetitle{RN11}} by \citeauthor{RN11}} \\
In \citeyear{RN11} \citeauthor{RN11} \cite{RN11} provided an analyses of the vulnerabilities of the GPS signal to spoofing attacks including the
satellite signal itself. \citeauthor{RN11} also proposed anti-spoofing algorithms and provided simulations to showcase the efffectiness of these
algorithms. In general only anti-spoofing methods that could be processed in software without modification to the receiver itself were considered.
In summary there were 10 anti-spoofing methods discussed in the paper; \todo{include summary table} 
\begin{enumerate}
    \item Monitor absolute power of each carrier: \\
    Since the expected reception power of a carrier is approximately $-155 dBm$. Using this a reasonable maximum power
    can be set.
    \item Monitor signal change in power: \\
    Since transmitted power satisfies equation \ref{eq:Power_tx} it can be seen that the received power will be altered significantly by a change in
    distance to the source. Therefore, a sudden change in recieved power could be an indication of attemtped spoofing. However since the received power
    is dependant on other variables like the environment and path that the signal takes, this method is ideally used for static obervations.
    \begin{equation} \label{eq:Power_tx}
        P_{tx}=P_{rx}r^2
    \end{equation}
    \item Monitor the reletive power: \\
    This method uses the power ratios of different frequency bands to determine spoof activity. As an example there is a $~3dB$ difference between
    the L1 and L2 band signals typically. If the observed power ratio is too far outside of this range then it can be assumed that there is a spoofing
    attack underway. It should be mentioned that ionosphere refraction may also affect the power ratio and should be taken into account.
    \item Bound and compare range rates: \\ 
    Since a moving receiver's phase movement is out of the spoofers control the code and phase range rates can be compared to detect spoofing. 
    Bounding these rates can add to the ability to detect spoofing activity.
    \item Doppler shift check: \\
    It is impossible for the spoofing attack to ccmpletly replicate all of the Doppler shifts for all satellites using a single transmitting antenna.
    Therefore, it would be necessary to have as many antenna as there are satellites which make it prohibitive from a spoofing standpoint. This can be
    used to test for spoofing activity.
    \item Cross correlation of L1 and L2: \\
    Based on the way that the GPS frequency bands operate, a cross correlation of L1 and L2 bands should result in a single peak, and due to the 
    difference in signal speed the sign of the cross correlation is known. This method will be unsuccessful if the spoofed is spoofing both carriers.
    \item Residual Analysis: \\
    Under spoofing conditions the recieved signal will be a combination of the authentic signal, the spoofed signal and random noise. The spoofed signal
    can be removed and if the ratio between the spoofed signal and authentic signal is low enough then the authentic signal can be recovered, otherwise
    the authentic signal is lost. 
    \item L1-L2 range differences
    \item Verify received ephemeris data: \\
    By compaing the recieved ephemeris data to known ephemeris and almanac data the spoofer will be unable to use its own position as stand in. 
    \item Jump detection : \\
    This method is based around tracking all observables and if there is a "Jump" in a specific observable this could indicate a spoofing attack.
\end{enumerate} 
Many of these methods must co-exist and can be used together to create a more robust anti-spoofing solution. For example if the absolute power is 
not limited, then the residual test will not be of use. It should be noted that while the presence of a spoofer can be determined, and hence 
throw away the related positional data, there has not been any method provided to re-determine the correct position. Therefore, in the case that
spoofing is detected, the attack will become a jamming attack.

Given that this paper was released in \citeyear{RN11} some of this infomation is outdated. For example it was concluded that GPS spoofing was not formidable
since it could be easily detected. With the advent and advnacement of SDR platforms
GPS spoofing hardware has become highly performant and affordable as well, with practical examples of spoofing attacks being \todo{insert reference} documented. 
However this paper provides a very good basis for building more complicated spoofing and anti-spoofing techniques since the underlying GPS system is
reletively unchanged. 

\medskip

\textbf{\emph{\citetitle{RN19}} by \citeauthor{RN19}} \\
In \citeyear{RN19} \citeauthor{RN19} \cite{RN19} devised a conceptual method for retrofitting anti-spoofing techniques to GPS devices without the need
to alter the software or hardware of those devices. This device is called a GPS assimilator and can also be used for increasing the accuracy and robustness
of the PVT in weak-signal environments. From a high level the assimilator will contain an RF front end with multi system receiver and navigation and timeing fusion module,  
anti-spoofing modules and an embedded GPS signal simulator. Conceptually this device will be placed between the RF antenna and the GPS receiver. The assimilator thus performs
all necessary signal processing to output an L1 C/A signal that the target GPS receiver will be able to interperet with accurate PVT data. The assimilator
can be used with many location systems including multiple GNSS constellations and cellular connections. Three use cases were included in the paper.
These are to protect the time reference receiver from an unsophisticated spoofing attack, reducing the ionospheric error in single frequency target
receivers and weak-signal tracking via CDMA cellular signal aiding. It was found that in each of these use cases the assimilator was able to improve
the ability of the target reciver to provide accurate PVT data.

By having a seperate inline component, especially one based off of SDR technologies, upgrades can be applied to any GPS receiver without needing to
make modifications to the existing system. This reduces cost and complexity of upgrading now and in the future as GPS anti-spoofing technology changes.
By using an assimilator a simple single frequency single constellation reciver can be upgraded to be a multi-frequency, multi-constellation receiver.

Future work on the assimilator include miniturising the design in order to fit inside of an antenna such that a user would be able to include all of the 
benefits of using the assimilator by only needing to chnage the antenna used. 

%-----------------------------------
%	SUBsubSECTION 3
%-----------------------------------

\subsubsection{Other References}

\textbf{\emph{Design of complete Software GPS Simulator with low complexity and precise Multipath Channel model} by A. Elango et al.} \\ 
In 2016 A. Elango proposed a completly software based approch to simulating GPS singals \cite{RN15}. A summary of the difference between analog
and digital based simulation systems is provided, with justification for producing a softawre based solution. In this proposal the GPS signals are created
using a custom piece of software. The output of this software is a message that has already been moudlated, which is saved into a file on the local
storage device. This was then fed into a MATLAB simulation environment for testing. The psudo code for the development of the program is include in
the publication, and provides a good resource for breaking down the message structure for GPS.

\medskip

%-----------------------------------
%	SUBSECTION 3
%-----------------------------------

\subsection{Literature Review methodology}
\begin{itemize}
    \item Exclusion criteria \\ To help narrow the scope of the literature review certain criteria was selected to be ommited
    \begin{itemize}
        \item Age of source: > 2010 for SDR specific | > 2008 for all others \\ When it comes to the implementation of spoofers using SDR platforms, the most up to date inforamtion is requried since the software typically used in these cases are open source and prone to frequent changes.\\ This is less of an issue when detailing the operationa of the GPS navigation system, or, to a lesser extent, effective spoofing attacks and defences. This is because most off the shelf receivers have not got any spoof mitigation built into their designs \cite{RN12}.
    \end{itemize}
    \item Inclusion criteria
    \begin{itemize}
        \item Application specifics \\ While not all sources will have an application, whether to attack or defend, it should be noted that there was an importance placed on getting sources that applied the theory described.
        \item SDR implementation \\ Since this project relied on the use of an SDR platform for the application of a spoofer it was important that a large number of sources also use a similar platform. This helped in forming a strategy to compolete the project. It was also important so that time was not wasted reinventing the wheel.
    \end{itemize}
    \item Keywords
    \begin{itemize}
        \item GPS
        \item GPS Spoofing
        \item GNSS Spoofing defence
        \item GPS UAV Attack
        \item GPS Spoof mitigation
        \item GPS Spoofing autonomous vehicles
        \item meaconing
    \end{itemize}
\end{itemize}

\subsubsection{Finding sources}
An effective method used to find appropriate sources was to find a recent paper that may not be appropriate but still relevant and to carefully look through
the reference list. By applying the list of exlusion and inclusions as above suitable sources could be found.

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Spoof Attacks}

%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------

\section{Spoof Defence}

%----------------------------------------------------------------------------------------
%	SECTION 4
%----------------------------------------------------------------------------------------

\section{GPS Threat Analysis}
\todo{This might be better suited to being the first Section after the Introduction}
As shown in Table \ref{tab:AttackSum}

\medskip

\begin{table}
    \begin{center}
        \caption{Summary of attack and defence strategies}
        \label{tab:AttackSum}
        \begin{tabular}{ |m{1cm}|m{3cm}|m{5cm}|m{3cm}| }
            \hline
            \textbf{No.} & \textbf{Author} & \textbf{Paper Title} & \textbf{Attack, Detection or Mitigation} \\
            \hline
            1 & \citeauthor{RN7} & \citetitle{RN7} & Mitigation \\
            \hline
            2 & \citeauthor{RN4} & \citetitle{RN4} & Attack \\
            \hline
        \end{tabular}
    \end{center}
\end{table}
